### 2023-11-09 manuscript/manuscript.Rmd
clarify replicated classes

Here, we outline the development of a data-driven, automated approach for 'first pass' putative molecular formula assignment in non-targeted ESI-MS fingerprinting and LC-MS profiling-based metabolomics data. 
This is aimed at biological experiments that include numerous replicates of sample classes for the assignment of low accurate mass (< 1000 atomic mass units (amu)) metabolite elemental compositions of biological origin.
It is an ensemble approach that combines a number of annotation strategies including correlation analysis, molecular formula selection, adduct and isotopic scoring and graphical component selection.
This is accompanied by the development of the R package *assignments* as an implementation of the approach.

>>>>

Here, we outline the development of a data-driven, automated approach for 'first pass' putative molecular formula assignment in non-targeted ESI-MS fingerprinting and LC-MS profiling-based metabolomics data. 
This is aimed at biological experiments that includes replicated samples (> 4) of experimental classes for the assignment of low accurate mass (< 1000 atomic mass units (amu)) metabolite elemental compositions of biological origin.
It is an ensemble approach that combines a number of annotation strategies including correlation analysis, molecular formula selection, adduct and isotopic scoring and graphical component selection.
This is accompanied by the development of the R package *assignments* as an implementation of the approach.
